Case study validations of automatic bullet matching

### 2018-10-10 index.Rmd
added references

There are several approaches for potential improvements: we can try to fine tune the matching algorithm to take make and model of the firearm and ammunition used into account or expand the traing of the algorithm to include a wider variety of makes and models. The downside of this is that we need to considerably expand the database used for training.

Another solution would be to expand on the aggregation used to get from land-to-land scores to bullet scores: SAM scores only take the scores of the maximum sequence into account and ignore scores associated with pairs of land engraved areas from different sources. Those scores might be useful in establishing a baseline that better expresses similarity between pairs of bullets.

>>>>

There are several approaches for potential improvements: we can try to fine tune the matching algorithm to take make and model of the firearm and ammunition used into account or expand the trainings base of the algorithm to include a wider variety of makes and models. The downside of this is that we need to considerably expand the database used for training.

Another solution would be to expand on the aggregation used to get from land-to-land scores to bullet scores: SAM scores only take the scores of the maximum sequence into account and ignore scores associated with pairs of land engraved areas from different sources. Those scores might be useful in establishing a baseline that better expresses similarity between pairs of bullets. One approach that uses scores for both same source pairs and different source pairs are score-based likelihood ratios \citep{Bunch:2013if, Morrison:2018fh}.
\citet{Morrison:2018km}  stress the need to additionally include the typicality of a signature.
